|

### 2025-01-31 doc/paper.qmd
paper upd

# Task 1 - Replication of Key Tables and Figures {#sec-task1}
Task 1 is the most comprehensive, replicating the methodology of key tables and figures from @ball_how_2008 using daily US stock return data (1972–2006) to establish baseline results, ensuring alignment with the original findings before extending the analysis in @sec-task2. By reconstructing Table 1 (Panel A), Table 2 (all panels), and Figure 1 (all panels), this task evaluates the robustness of the original results and identifies potential discrepancies, offering insights into data consistency, methodology, and market dynamics over the examined period. The use of daily CRSP data is essential for capturing short-term stock price movements around earnings announcements, ensuring precise event window calculations. The discussion of replication findings is presented in @sec-results1.

@@

1. Following @ball_how_2008, I define earnings announcement windows as the three-day period surrounding the earnings release (-1 to +1), where Day -1 is the last trading day before the announcement, Day 0 is the announcement day, and Day +1 is the first trading day after the announcement. According to @center_for_research_in_security_prices_crsp_crsp_2024 guide, data are never provided on weekends or trading holidays, meaning there is no need for manual filtering of such days. However, if an earnings announcement falls on a non-trading day, adjustments are necessary to maintain the three-day window. Hence, earnings announcement dates are first extracted from Compustat and then matched with CRSP trading data to obtain stock returns for the event window (-1, 0, +1). If Day 0 falls on a weekend or holiday, it is shifted to the next available trading day. Similarly, if Day -1 or Day +1 is unavailable due to a non-trading day, the nearest prior or next trading day, respectively, is used to preserve the event window. This adjustment prevents shortening the window, ensuring a complete three-day period for capturing the full market response to earnings announcements.

@@

5. The replication relies on Compustat and CRSP, linked via the CRSP/Compustat Merged (CCM) database, but with different update frequencies: Compustat (daily), CRSP (annually), and CCM (annually). Timing mismatches may arise, especially for firms with restated financials, leading to slight variations in event window alignment when calculating earnings-announcement returns. Unlike the original study, this replication uses the latest WRDS version available as of January 2025, meaning database updates may cause minor differences in firm coverage or reported values.

@@

By following the steps outlined in @sec-replication_steps1 and adhering to the assumptions made, I successfully replicated the results from @ball_how_2008. A thorough step-by-step approach, with each step clearly documented, helps to understand and verify the outputs.

@@

**Step 1: Pulling the Data and Managing the Databases**  
Data is pulled from the `crsp_a_ccm.ccmxpf_lnkhist`, `crsp_a_stock.dsf`, `comp_na_daily_all.fundq` tables via WRDS, using Python for data processing and regression analysis and facilitating direct access to stock price and return data from CRSP alongside firm fundamentals from Compustat, enabling a seamless link between market and accounting data. Visual Studio Code was used as the Integrated Development Environment (IDE) for writing, debugging, and optimizing the Python code. While WRDS provides extensive financial datasets, documentation on precise variable selection and dataset integration is limited, requiring additional validation and cross-referencing with prior research.

This Assignment involves pulling data directly from the Audit Analytics database and preparing the data for further analysis from raw data to final output.

To ensure data relevance, the pulling process was restricted to data for the year 2021. The variable `trans_report_auditor_state` was used to filter the data to include only audit firms associated with the specific EU and EEA countries, as specified in configuration file `config/pull_data_cfg​`. This filtering step ensured that the analysis focuses on audit market concentration within the geographical scope and year range as defined by @EC_Report_2024.

@@

# Conclusion {#sec-conclusion}
This project effectively demonstrates the use of a systematic and collaborative workflow for empirical accounting research, leveraging the TRR 266 Template for Reproducible Empirical Accounting Research. By following an open science approach, I successfully replicated key tables and figures from @ball_how_2008, providing insights into how earnings announcements contribute to price formation and market efficiency. While exact replications often yield different samples and outcomes due to dataset updates or methodological variations, my results align closely with the statistics presented in the original study, reinforcing the reliability of the replication process. Moreover, by extending the analysis beyond the original study’s U.S. market focus, the project highlights how market structures and investor behaviors influence the informativeness of earnings disclosures in different jurisdictions.

>>>>

# Task 1 - Replication of Key Tables and Figures {#sec-task1}
Task 1 is the most comprehensive, replicating the methodology of key tables and figures from @ball_how_2008 using daily US stock return data (1972–2006) to establish baseline results, ensuring alignment with the original findings before extending the analysis in @sec-task2. By reconstructing Table 1 (Panel A), Table 2 (all panels), and Figure 1 (all panels), the task evaluates the robustness of the original results and identifies potential discrepancies, offering insights into data consistency, methodology, and market dynamics over the examined period. The use of daily CRSP data is essential for capturing short-term stock price movements around earnings announcements, ensuring precise event window calculations. The discussion of replication findings is presented in @sec-results1.

@@

1. Following @ball_how_2008, I define earnings announcement windows as the three-day period surrounding the earnings release (-1 to +1), where Day -1 is the last trading day before the announcement, Day 0 is the announcement day, and Day +1 is the first trading day after the announcement. According to @center_for_research_in_security_prices_crsp_crsp_2024 guide, data are never provided on weekends or trading holidays, meaning there is no need for manual filtering of such days. However, if an earnings announcement falls on a non-trading day, adjustments are necessary to maintain the three-day window. Hence, earnings announcement dates are first extracted from Compustat and then matched with CRSP trading data to obtain stock returns for the event window (-1, 0, +1). If Day 0 falls on a weekend or holiday, it is shifted to the next available trading day. Similarly, if Day -1 or Day +1 is unavailable due to a non-trading day, the nearest prior or next trading day, respectively, is used to preserve the event window.

@@

5. The replication relies on Compustat and CRSP, linked via the CRSP/Compustat Merged (CCM) database, but with different update frequencies: Compustat (daily), CRSP (annually), and CCM (annually). Timing mismatches may arise, especially for firms with restated financials, leading to possible variations in event window alignment when calculating earnings-announcement returns. Unlike the original study, this replication uses the latest WRDS version available as of January 2025, meaning database updates may cause differences in firm coverage or reported values.

@@

By following the steps outlined in @sec-replication_steps1 and adhering to the assumptions made, I aim to replicate the results from @ball_how_2008. A thorough step-by-step approach, with each step clearly documented, helps to understand and verify the outputs.

@@

**Step 1: Pulling the Data and Managing the Databases**  
Data is pulled from WRDS using Python to integrate daily stock returns from CRSP (`crsp_a_stock.dsf`) with quarterly earnings announcement data from Compustat (`comp_na_daily_all.fundq`), linked via the Compustat-CRSP link table (`crsp_a_ccm.ccmxpf_lnkhist`). `permno` identifier matches stock returns to firm fundamentals via `gvkey` for exact firm/year match. Key variables include `ret` (daily stock return) and `rdq` (earnings announcement date), enabling event study analysis from 1972 to 2023. While WRDS provides extensive financial datasets, documentation on precise variable selection and dataset integration is limited, requiring additional validation and cross-referencing with prior research.

The data is pulled for the entire range 1972-2023 required for Task 1 and 2 to prevent double preparation step.

@@

# Conclusion {#sec-conclusion}
This project effectively demonstrates the use of a systematic and collaborative workflow for empirical accounting research, leveraging the TRR 266 Template for Reproducible Empirical Accounting Research. By following an open science approach, I aimed to replicate key tables and figures from @ball_how_2008, providing insights into how earnings announcements contribute to price formation and market efficiency. While exact replications often yield different samples and outcomes due to dataset updates or methodological variations, my results align closely with the statistics presented in the original study, reinforcing the reliability of the replication process. Moreover, by extending the analysis beyond the original study’s U.S. market focus, the project highlights how market structures and investor behaviors influence the informativeness of earnings disclosures in different jurisdictions.
